Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-10-06 paper.tex
Update paper.tex

This paper investigates the microscopic parameters that control HDFG output. \cite{RN352, Bonn2024, McDonnell2024}
HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the results are similar.
We note that HDFG emission can be phase-matched in media with normal dispersion while HSFG cannot,\cite{RN279, RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments. \cite{Kaufman2024}  
In \autoref{steadystate}, we first identify the vibrational selection rules. 
The selection rules of electronically-resonant HDFG are then identified through an expansion of electronic dipole moments following Chung and Ziegler.\cite{Ziegler1988}
HDFG is found to be allowed in any harmonic system that has infrared active vibrations.
A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
After developing selection rules, some quantitative aspects of HDFG are discussed in \autoref{quant}.

@@

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation $via$
\begin{equation}\label{LVNE}
	\dot{\rho}^{(n)} = \frac{1}{i \hbar} [H + V(t), \rho^{(n-1)}] + \dot{\rho}^{(n)}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ becomes a complex function that can be modified to include phenomena such as system-bath interactions, solvent-solute coupling, among others. \cite{Sung2001}
In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e. exponential relaxation, where $\Gamma$ is the system's dephasing rate. \cite{RN455, Sue1986, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$.
The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times. \cite{Raschke2002, Gaynor2017}

It is useful to briefly discuss the impact of time ordering on HDFG output.
Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.\cite{Cho2008}
While we have only isolated one specific HDFG resonance and time-ordering scheme (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
If $\omega_2$ becomes resonant and $\omega_1$ becomes non-resonant, where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the pathways presented in \autoref{fig:sivewmel2} will interfere, which can amplify or obscure coherent output.
\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66 in]{figures/timeorderedwmel.png}
	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 
		The states are labeled as $\ket{a,b}$, where $a$ refers to an electronic state and $b$ refers to quanta in a vibration on $a$, described in \autoref{Albrecht}.
		In all cases, $\omega_2 > \omega_1$.
		The virtual states are arbitrarily placed and fluctuate in energy dependent upon the energy of the input fields.
	}
	\label{fig:sivewmel2}
\end{figure*}

>>>>

This paper investigates the microscopic parameters that control HDFG output. \cite{RN352, Bonn2024, McDonnell2024}
HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the results are similar.
We note that HDFG emission can be phase-matched in media with normal dispersion while HSFG cannot.\cite{RN279, RN278} 
In \autoref{steadystate}, we first identify the vibrational selection rules. 
The selection rules of electronically-resonant HDFG are then identified through an expansion of electronic dipole moments following Chung and Ziegler.\cite{Ziegler1988}
HDFG is found to be allowed in any harmonic system that has infrared active vibrations.
A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
After developing selection rules, some quantitative aspects of HDFG are discussed in \autoref{quant}.

@@

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation:
\begin{equation}\label{LVNE}
	\dot{\rho}^{(n)} = \frac{1}{i \hbar} [H + V(t), \rho^{(n-1)}] + \dot{\rho}^{(n)}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
In systems where interactions with surroundings are relevant, expressions for $\dot{\rho}_R$ may be quite complicated due to intricate phenomena such as system-bath interactions and solvent-solute coupling, among others. \cite{Sung2001}
In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write a time-independent relaxation matrix $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e. exponential relaxation, where $\Gamma$ is the system's dephasing rate. \cite{RN455, Sue1986, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$.
The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times. \cite{Raschke2002, Gaynor2017}

It is useful to briefly discuss the impact of time ordering on HDFG output.
Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.\cite{Cho2008}
While we have only isolated one specific HDFG resonance and time-ordering scheme (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
If $\omega_2$ becomes resonant and $\omega_1$ becomes non-resonant, where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the pathways presented in \autoref{fig:sivewmel2} will interfere, which can amplify or obscure coherent output.
\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=\textwidth / 2]{figures/timeorderedwmel.png}
	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 
		The states are labeled as $\ket{a,b}$, where $a$ refers to an electronic state and $b$ refers to quanta in a vibration on $a$, described in \autoref{Albrecht}.
		In all cases, $\omega_2 > \omega_1$.
		The virtual states are arbitrarily placed and fluctuate in energy dependent upon the energy of the input fields.
	}
	\label{fig:sivewmel2}
\end{figure*}
